Parenting observation lexical diversity

### 2017-07-20 parenting_obs_lexdiv.Rmd
update readme

```{r}
data <- read.csv("data.csv", header =TRUE)
dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData")

>>>>

```{r}
data <- read.csv("lexdiv_data.csv", header =TRUE)
dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData")
